Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-12-23 main.tex
editing IV-B, enlarged some of the figures in the experiments section (still at 10 pages)

We design three variants of memory-aware HEFT:
\begin{itemize}
\item    
  HEFTM-BL orders tasks by non-increasing bottom levels, where the bottom
  level is defined as
  $$bl(u) = w_u + \max_{(u,v)\in E} \{c_{u,v} + bl(v)\}$$
  (the max is 0 if there is no outgoing edge).

\item    
  HEFTM-BLC %: from the study of the fork (see below), it seems important
  %  to also account for the size of the data as input of a task,
  is  giving more priority at tasks with potential large incoming communications,
  hence aiming at clearing the memory used by files as soon as possible,
  to have more free memory for remaining tasks to be executed on the processor.
  Therefore, for each task, we compute a modified bottom level accounting for communications:
  $$blc(u) = w_u + \max_{(u,w)\in E} \{c_{u,w} + blc(w)\} + \max_{(v,u)\in E} c_{v,u}   . $$

@@

\item   
  Finally, HEFTM-MM orders tasks  in the order returned by %as dictated by MinMem.
  the  \algo{memDag} algorithm~\cite{KAYAASLAN20181}, which corresponds to a traversal
  of the graph that minimizes the peak memory usage.
\end{itemize}

@@

    Then, the idea is to pick the next free task in the given order,
    and greedily assign it to a processor, by trying all possible options
    and keeping the most promising one. We first detail how a task
    is tentatively assigned on a processor, by carefully accounting for the memory usage.
    Next, we explain the steps to be taken to effectively assign a task on a given processor.

@@

    \begin{figure}[tb]
        \centering
        \includegraphics[width=0.9\columnwidth] {images/success-rates-large}
        \caption{Success rates on the default cluster. Higher is better.}
        \label{fig:success-rates-large}
        \vspace{-0.3cm}
    \end{figure}

@@

    \begin{figure}[tb]
        \centering
        \includegraphics[width=0.8\columnwidth] {images/UpdatesMss2}
        \caption{Relative (excess) makespan of \heftbl, \heftblc and \heftmm. Smaller is better.}
        \label{fig:updates-ms}
        \vspace{-0.3cm}
    \end{figure}

>>>>

Our three variants of memory-aware HEFT work as follows:
\begin{itemize}
\item    
  HEFTM-BL orders tasks by non-increasing bottom levels, where the bottom
  level is defined as
  $$bl(u) = w_u + \max_{(u,v)\in E} \{c_{u,v} + bl(v)\}$$
  (max yields $0$ if there is no outgoing edge).

\item    
  HEFTM-BLC %: from the study of the fork (see below), it seems important
  %  to also account for the size of the data as input of a task,
  gives more priority to tasks with potential large incoming communications,
  hence aiming at clearing the memory used by files as soon as possible,
  to have more free memory for remaining tasks to be executed on the processor.
  Therefore, for each task, we compute a modified bottom level accounting for communications:
  $$blc(u) = w_u + \max_{(u,w)\in E} \{c_{u,w} + blc(w)\} + \max_{(v,u)\in E} c_{v,u}   . $$

@@

\item   
  Finally, HEFTM-MM orders tasks  in the order returned by %as dictated by MinMem.
  the  \algo{memDag} algorithm~\cite{KAYAASLAN20181}, which corresponds to a traversal
  of the graph that minimizes peak memory usage.
\end{itemize}

@@

Then, the idea is to pick the next free task in the given order,
and greedily assign it to a processor, by trying all possible options
and keeping the most promising one. We first detail how a task
is tentatively assigned to a processor, by carefully accounting for the memory usage.
Next, we explain the steps to be taken to effectively assign a task to a given processor.

@@

    \begin{figure}[tb]
        \centering
        \includegraphics[width=0.99\columnwidth] {images/success-rates-large}
        \caption{Success rates on the default cluster. Higher is better.}
        \label{fig:success-rates-large}
        \vspace{-0.3cm}
    \end{figure}

@@

    \begin{figure}[tb]
        \centering
        \includegraphics[width=0.95\columnwidth] {images/UpdatesMss2}
        \caption{Relative (excess) makespan of \heftbl, \heftblc and \heftmm. Smaller is better.}
        \label{fig:updates-ms}
        \vspace{-0.3cm}
    \end{figure}
